---
title: "time intervals"
output: html_notebook
---

# Sample data frame to check chunk output style
```{r}
Name <- c("Jon", "Bill", "Maria", "Ben", "Tina")
Age <- c(23, 41, 32, 58, 26)

df <- data.frame(Name, Age)

df
```


Vacancies
Part 1 Include central tendency and variation by subject, grade, grade-subject, campus, campus-subject, region, region-subject

a) subject    (col: course credit type)
b) grade 
c) grade-subject
d) campus
e) campus-subject
f) region
g) region-subject

#1) How long are vacancies (median and mean and SD)?
#2) How many vacancies (median, mean and SD)?
#3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
#4) Add box plots and histograms.


---------
FOCUS of this experiment code is on q#3, will try to work out proof-of-concept on "month" time intervals
------

```{r}
#library(janitor)
library(tidyverse)
library(lubridate)

```

load vacancies from CSV
#read from actual Idea tables with edison scripts
```{r}
# load from CSV
#jobvite_staffing_vacancies <- read.csv("data/export_from_maura/jobvite_staffing_vacancies_export_2024-10-06.csv", header=TRUE)

# fix data types for date columns
jobvite_staffing_vacancies$hire_date <- as.Date(jobvite_staffing_vacancies$hire_date, tryFormats = c("%m/%d/%y"))
jobvite_staffing_vacancies$work_start_date <- as.Date(jobvite_staffing_vacancies$work_start_date)
jobvite_staffing_vacancies$work_end_date <- as.Date(jobvite_staffing_vacancies$work_end_date)
jobvite_staffing_vacancies$termination_date <- as.Date(jobvite_staffing_vacancies$termination_date)
jobvite_staffing_vacancies$job_most_recent_open_date <- as.Date(jobvite_staffing_vacancies$job_most_recent_open_date)
jobvite_staffing_vacancies$vacancy_begining_start_date <- as.Date(jobvite_staffing_vacancies$vacancy_begining_start_date)
jobvite_staffing_vacancies$vacancy_begining_end_date <- as.Date(jobvite_staffing_vacancies$vacancy_begining_end_date)
jobvite_staffing_vacancies$total_days_vacancy <- as.numeric(jobvite_staffing_vacancies$total_days_vacancy)

#jobvite_staffing_vacancies
#glimpse(jobvite_staffing_vacancies)

# limit to fewer/relevant columns for purposes of interval experiments
jobvite_staffing_vacancies_trimmed <- jobvite_staffing_vacancies %>%
  select(vacancy_begining_start_date, vacancy_begining_end_date, total_days_vacancy)

glimpse(jobvite_staffing_vacancies_trimmed)

```


q3 time intervals


# temporary code experiment with single hardcoded interval stored in variable
#DO NOT USE THIS CODE CHUNK (was initial experiment without a helper function)
```{r}

#vacancies_exp1 <- jobvite_staffing_vacancies_trimmed
vacancies_exp1 <- jobvite_staffing_vacancies

# experiment with single hardcoded interval
interval_start = as.Date("2023-08-01")
interval_end = as.Date("2023-08-08")
new_col_label = "8/01 to 8/08"


# note: a vacancy counts toward a specific interval (e.g. month of Oct) if any portion of the vacancy occurs in the interval
# in other words:
#       IF vacancy_start is inside the interval
#       OR vacancy_end is inside the interval
#       OR interval is fully inside of the vacancy (i.e. vacancy_start is before the interval AND vacancy_end is after the interval) 
vacancies_exp1 <- mutate(vacancies_exp1, !!new_col_label := 
                             # vacancy_start is inside the interval
                             (interval_start <= vacancies_exp1$vacancy_begining_start_date & vacancies_exp1$vacancy_begining_start_date < interval_end)
                            # vacancy_end is inside the interval
                           | (interval_start <= vacancies_exp1$vacancy_begining_end_date & vacancies_exp1$vacancy_begining_end_date < interval_end)
                           # interval is fully inside of the vacancy
                           | (vacancies_exp1$vacancy_begining_start_date < interval_start & vacancies_exp1$vacancy_begining_end_date >= interval_end)
                           )
vacancies_exp1
                             

```

# temporary code experiment with helper function for interval check - practice
---------
#this helper function is one of the key parts of the code, but the DEMO usage underneath is still temporary.
#  ... actual usage for month and week intervals is in following chunks
```{r}


# Helper Function: checks the vacancies in the data frame (cols: "vacancy_begining_start_date" and "vacancy_begining_end_date") and adds a TRUE/FALSE column for whether that vacancy has any overlap with the provided interval_start and interval_end.
# note: a vacancy counts toward a specific interval (e.g. month of Oct) if any portion of the vacancy occurs in the interval
# in other words:
#       IF vacancy_start is inside the interval
#       OR vacancy_end is inside the interval
#       OR interval is fully inside of the vacancy (i.e. vacancy_start is before the interval AND vacancy_end is after the interval) 

addVacancyIntervalCol <- function(df, interval_start, interval_end, new_col_label)
{
  mutate(df, !!new_col_label := 
                             # vacancy_start is inside the interval
                             (interval_start <= df$vacancy_begining_start_date & df$vacancy_begining_start_date < interval_end)
                            # vacancy_end is inside the interval
                           | (interval_start <= df$vacancy_begining_end_date & df$vacancy_begining_end_date < interval_end)
                           # interval is fully inside of the vacancy
                           | (df$vacancy_begining_start_date < interval_start & df$vacancy_begining_end_date >= interval_end)
                           )
}


# DEMO usage on single manually defined interval
# BETTER usage with lists/loops in later chunks

# data frame to work on
#vacancies_exp2 <- jobvite_staffing_vacancies_trimmed
vacancies_exp2 <- jobvite_staffing_vacancies


# experiment with function call with single hardcoded interval
interval_start = as.Date("2023-08-01")
interval_end = as.Date("2023-08-08")
new_col_label = "8/01 to 8/08"

# note picked out 8/01 to 8/08 as a test-case interval since there were vacancy rows/results in the data that would validate each part of the helper function logic (i.e. start vacancy in interval, end vacancy in interval, and overlap full interval)

# call function
vacancies_exp2 <- addVacancyIntervalCol(vacancies_exp2, interval_start, interval_end, new_col_label)
vacancies_exp2 <- addVacancyIntervalCol(vacancies_exp2, as.Date("2023-08-08"), as.Date("2023-08-15"), "8/08 to 8/15")

# check output
vacancies_exp2


```

experiment, making list of intervals and labels
# this is for month interval (use helper function from previous chunk)
# MONTH

```{r}
# uses helper function "addVacancyIntervalCol" defined in earlier chunk

month_intervals_23_24 = data.frame(
  # label = character(), # will populate in next step based on dates
  start_interval = seq.Date(from = as.Date("2023-07-01"), to = as.Date("2024-06-01"), by = "month"),
  end_interval = seq.Date(from = as.Date("2023-08-01"), to = as.Date("2024-07-01"), by = "month")
)
# add "label" column, with 3 letter month abbrev (e.g. "Feb") ... year implied (include in plot title/labels)
month_intervals_23_24 <- month_intervals_23_24 %>%
    mutate( label = format(month_intervals_23_24$start_interval, "%b"))

month_intervals_23_24


# now use interval list: loop thru and add columns to vacancies table

# data frame to work on
#vacancies_exp3 <- jobvite_staffing_vacancies_trimmed
vacancies_exp3 <- jobvite_staffing_vacancies

for (i in 1:nrow(month_intervals_23_24))
{
  #print(month_intervals_23_24[i, "start_interval"])
  vacancies_exp3 <- addVacancyIntervalCol(vacancies_exp3, month_intervals_23_24[i,"start_interval"], month_intervals_23_24[i,"end_interval"], month_intervals_23_24[i,"label"])
}
vacancies_exp3

# col labels containing the vacancy intervals
month_intervals_23_24["label"]


#
# count vacancies per interval
#
list(month_intervals_23_24["label"])

#-----------------------------
#OUTPUT of Months, with various groupings 

#overall (no groupings) (months only)
vacancy_interval_counts_months <- vacancies_exp3 %>%
  # TODO: other grouping, eg. by region
  #select(all_of(month_intervals_23_24[["label"]]))
   summarise(across(all_of(month_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_months

#Region
vacancy_interval_counts_months_region <- vacancies_exp3 %>%
  # TODO: other grouping, eg. by region
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  group_by(Region) %>%
  #select(all_of(month_intervals_23_24[["label"]]))
   summarise(across(all_of(month_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_months_region

#--------------------------------------
#CAMPUS





#--------------------------
#SUBJECT

#prep Subject data for Month
subject <- vacancies_exp3 %>%
  # TODO: other grouping, eg. by region
   mutate("Vacancy Length in Days" = total_days_vacancy) %>%
  mutate(Campus = campus_upper) %>%
  mutate(Subject = job_title) %>%
   mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  filter(Subject != "Executive Campus Leadership") 
subject

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Math"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Science"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - English Language Arts"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Social Studies"] <- "Social Studies"

#Change data from character to numeric (col Hired)
#job_1920$Hired <- as.numeric(job_1920$Hired)

#Change data from character to numeric (col Hired)
subject$Subject <- as.character(subject$Subject)
subject

#distinct subjects
subject_distinct2 <- subject %>%
  select(Subject) %>%
  distinct()
subject_distinct2


#Month/Subject - OUTPUT
vacancy_interval_counts_months_subject <- subject %>%
group_by(Subject) %>%
  #select(all_of(month_intervals_23_24[["label"]]))
   summarise(across(all_of(month_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_months_subject

```

#MONTH
#GRAPH
#MONTH
```{r}
#month- REGION

#region data
vacancy_interval_counts_months_region

#pivot_longer - (to make data in correct format for time-series line graphs)
vacancy_interval_counts_months_region <- vacancy_interval_counts_months_region %>%
pivot_longer(!Region, names_to = "Month", values_to = "Count")
vacancy_interval_counts_months_region


#put numbers ahead of month name (so plots in order)
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Jul"] <- "01 Jul"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Aug"] <- "02 Aug"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Sep"] <- "03 Sep"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Oct"] <- "04 Oct"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Nov"] <- "05 Nov"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Dec"] <- "06 Dec"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Jan"] <- "07 Jan"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Feb"] <- "08 Feb"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Mar"] <- "09 Mar"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Apr"] <- "10 Apr"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "May"] <- "11 May"
vacancy_interval_counts_months_region$Month[vacancy_interval_counts_months_region$Month == "Jun"] <- "12 Jun"



#libraries
library(ideacolors)
library(ideadata)

#line graph
l_region_subject <- vacancy_interval_counts_months_region %>%
  ggplot(aes(x=Month, y=Count, group = Region, color = Region)) +
 geom_line() +
    #scale_color_viridis(discrete = TRUE) +
    #ggtitle("Number of Vacancies for Each Month by Subject") +
    #theme_ipsum() +
    #ylab("Number of Vacancies SY 23-24")

 scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   #theme(legend.position="none") +             #removes legend  (REF:https://r-charts.com/ggplot2/legend/ )
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Number of Vacancies",
       title = "Number of Vacancies by Region",
       subtitle = "for Each Month for SY 23-24")

l_region_subject







#-------------------------------------
#month- subject data
vacancy_interval_counts_months_subject


#pivot_longer - (to make data in correct format for time-series line graphs)
vac_interval_counts_months_subject <- vacancy_interval_counts_months_subject %>%
pivot_longer(!Subject, names_to = "Month", values_to = "Count")
vac_interval_counts_months_subject

#put numbers ahead of month name (so plots in order)
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Jul"] <- "01 Jul"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Aug"] <- "02 Aug"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Sep"] <- "03 Sep"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Oct"] <- "04 Oct"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Nov"] <- "05 Nov"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Dec"] <- "06 Dec"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Jan"] <- "07 Jan"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Feb"] <- "08 Feb"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Mar"] <- "09 Mar"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Apr"] <- "10 Apr"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "May"] <- "11 May"
vac_interval_counts_months_subject$Month[vac_interval_counts_months_subject$Month == "Jun"] <- "12 Jun"

vac_interval_counts_months_subject 
library(ideacolors)
library(ideadata)

#line graph
l_month_subject <- vac_interval_counts_months_subject %>%
  ggplot(aes(x=Month, y=Count, group = Subject, color = Subject)) +
 geom_line() +
    #scale_color_viridis(discrete = TRUE) +
    #ggtitle("Number of Vacancies for Each Month by Subject") +
    #theme_ipsum() +
    #ylab("Number of Vacancies SY 23-24")

 scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   #theme(legend.position="none") +             #removes legend  (REF:https://r-charts.com/ggplot2/legend/ )
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Number of Vacancies",
       title = "Number of Vacancies by Subject",
       subtitle = "for Each Month for SY 23-24")

l_month_subject

#--------------------------------------------
#EXAMPLE CODE
#REF: https://r-graph-gallery.com/line-chart-several-groups-ggplot2.html
#https://r-graph-gallery.com/line-chart-several-groups-ggplot2.html

# library(ggplot2)
# library(babynames) # provide the dataset: a dataframe called babynames
# library(dplyr)
# library(hrbrthemes)
# library(viridis)
# 
# # Keep only 3 names
# don <- babynames %>% 
#   filter(name %in% c("Ashley", "Patricia", "Helen")) %>%
#   filter(sex=="F")
# don
# # Plot
# don %>%
#   ggplot( aes(x=year, y=n, group=name, color=name)) +
#     geom_line() +
#     scale_color_viridis(discrete = TRUE) +
#     ggtitle("Popularity of American names in the previous 30 years") +
#     theme_ipsum() +
#     ylab("Number of babies born")

```



#WEEK

# experiment: by week intervals
#this is for week interval (use helper function from previous chunk)
```{r}
# uses helper function "addVacancyIntervalCol" defined in earlier chunk

# choosing to define week as Mon -> Mon (semi-arbitrary choice)
# first week interval Mon 2023-07-03 up to Mon 2023-07-10
# last week interval Mon 2024-06-03 up to Mon 2024-06-10
week_intervals_23_24 = data.frame(
  # label = character(), # will populate in next step based on dates
  start_interval = seq.Date(from = as.Date("2023-07-03"), to = as.Date("2024-06-03"), by = "week"),
  end_interval = seq.Date(from = as.Date("2023-07-10"), to = as.Date("2024-06-10"), by = "week")
)
# add "label" column, with " month/day (e.g. "7/03") ... Note: in plot axis label mention "week of Monday <>"
week_intervals_23_24 <- week_intervals_23_24 %>%
    mutate( label = format(week_intervals_23_24$start_interval, "%m/%d"))

week_intervals_23_24


# now use interval list: loop thru and add columns to vacancies table

# data frame to work on
#vacancies_exp4 <- jobvite_staffing_vacancies_trimmed
vacancies_exp4 <- jobvite_staffing_vacancies

for (i in 1:nrow(week_intervals_23_24))
{
  #print(month_intervals_23_24[i, "start_interval"])
  vacancies_exp4 <- addVacancyIntervalCol(vacancies_exp4, week_intervals_23_24[i,"start_interval"], week_intervals_23_24[i,"end_interval"], week_intervals_23_24[i,"label"])
}
vacancies_exp4

# col labels containing the vacancy intervals
week_intervals_23_24["label"]


#
# count vacancies per interval
#
list(week_intervals_23_24["label"])

#------------------
#OUTPUT by Week (and groupings)

vacancy_interval_counts_weeks_overall <- vacancies_exp4 %>%
  # TODO: other grouping, eg. by region
  #select(all_of(month_intervals_23_24[["label"]]))
  summarise(across(all_of(week_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_weeks_overall

#REGION  - week
vacancy_interval_counts_weeks_region <- vacancies_exp4 %>%
  # TODO: other grouping, eg. by region
  #select(all_of(month_intervals_23_24[["label"]]))
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  group_by(Region) %>%
  summarise(across(all_of(week_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_weeks_region

#-----------------
#CAMPUS - week



#--------------------
# SUBJECT - week

#prep Subject data for Month
subject <- vacancies_exp4 %>%
  # TODO: other grouping, eg. by region
   mutate("Vacancy Length in Days" = total_days_vacancy) %>%
  mutate(Campus = campus_upper) %>%
  mutate(Subject = job_title) %>%
   mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  filter(Subject != "Executive Campus Leadership") 
subject

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Math"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Science"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - English Language Arts"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Social Studies"] <- "Social Studies"

#Change data from character to numeric (col Hired)
#job_1920$Hired <- as.numeric(job_1920$Hired)

#Change data from character to numeric (col Hired)
subject$Subject <- as.character(subject$Subject)
subject

#Subject - week - OUTPUT
vacancy_interval_counts_weeks_subject <- subject %>%
  # TODO: other grouping, eg. by region
  #select(all_of(month_intervals_23_24[["label"]]))
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  group_by(Subject) %>%
  summarise(across(all_of(week_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_weeks_subject

```



experiment, making list of intervals and labels
# this is for Semester interval (use helper function from previous chunk)
# SEMESTER

```{r}
# uses helper function "addVacancyIntervalCol" defined in earlier chunk

#SEMESTER
semester_intervals_23_24 = data.frame(
  # label = character(), # will populate in next step based on dates
  start_interval = c("2023-08-01", "2024-01-02"),
  end_interval = c("2023-12-15", "2024-05-24"),
  label = c("Fall Semester", "Spring Semester")                 
  )

# now use interval list: loop thru and add columns to vacancies table

# data frame to work on
#vacancies_exp3 <- jobvite_staffing_vacancies_trimmed
vacancies_exp_sem <- jobvite_staffing_vacancies

for (i in 1:nrow(semester_intervals_23_24))
{
  #print(month_intervals_23_24[i, "start_interval"])
  vacancies_exp_sem <- addVacancyIntervalCol(vacancies_exp_sem, semester_intervals_23_24[i,"start_interval"], semester_intervals_23_24[i,"end_interval"], semester_intervals_23_24[i,"label"])
}
vacancies_exp_sem

# col labels containing the vacancy intervals
semester_intervals_23_24["label"]

# count vacancies per interval
list(semester_intervals_23_24["label"])

#-----------------------------
#OUTPUT of Months, with various groupings 
#SEMESTER

#overall (no groupings) (months only)
vacancy_interval_counts_sem <- vacancies_exp_sem %>%
  # TODO: other grouping, eg. by region
  #select(all_of(month_intervals_23_24[["label"]]))
   summarise(across(all_of(semester_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_sem

#-----------------------
#REGION 
#semester
vacancy_interval_counts_sem_region <- vacancies_exp_sem %>%
  # TODO: other grouping, eg. by region
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  group_by(Region) %>%
  #select(all_of(month_intervals_23_24[["label"]]))
   summarise(across(all_of(semester_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_sem_region

#-----------------------------
#CAMPUS




#---------------------
#Subject

#prep Subject data for Month
subject <- vacancies_exp_sem %>%
  # TODO: other grouping, eg. by region
   mutate("Vacancy Length in Days" = total_days_vacancy) %>%
  mutate(Campus = campus_upper) %>%
  mutate(Subject = job_title) %>%
   mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  filter(Subject != "Executive Campus Leadership") 
subject

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Math"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Science"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - English Language Arts"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Social Studies"] <- "Social Studies"
subject


#Change data from character to numeric (col Hired)
subject$Subject <- as.character(subject$Subject)
subject

#Subject - week - OUTPUT
vacancy_interval_counts_sem_subject <- subject %>%
  # TODO: other grouping, eg. by region
  #select(all_of(month_intervals_23_24[["label"]]))
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  group_by(Subject) %>%
  summarise(across(all_of(semester_intervals_23_24[["label"]]),sum))

vacancy_interval_counts_sem_subject #data looks good








```
#GRAPHS
#Time series graph
#REF: https://clauswilke.com/dataviz/time-series.html
```{r}

#SEMESTER
#region

#pivot_longer - (to make data in correct format for time-series line graphs)
vacancy_interval_counts_sem_region <- vacancy_interval_counts_sem_region %>%
pivot_longer(!Region, names_to = "Semester", values_to = "Count")
vacancy_interval_counts_sem_region


# #put numbers ahead of month name (so plots in order)
# vacancy_interval_counts_sem_region$Semester[vacancy_interval_counts_sem_region$Semester == "Jul"] <- "01 Jul"
# vacancy_interval_counts_sem_region$Semester[vacancy_interval_counts_sem_region$Semester == "Aug"] <- "02 Aug"
# 



#libraries
library(ideacolors)
library(ideadata)

#line graph
l_region_sem <- vacancy_interval_counts_sem_region %>%
  ggplot(aes(x=Semester, y=Count, group = Region, color = Region)) +
 geom_line() +
    #scale_color_viridis(discrete = TRUE) +
    #ggtitle("Number of Vacancies for Each Month by Subject") +
    #theme_ipsum() +
    #ylab("Number of Vacancies SY 23-24")

 scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   #theme(legend.position="none") +             #removes legend  (REF:https://r-charts.com/ggplot2/legend/ )
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Number of Vacancies",
       title = "Number of Vacancies by Region",
       subtitle = "for Each Semester for SY 23-24")

l_region_sem

#-------------------------------
#CAMPUS



#--------------------------
#SEMESTER
#region

#pivot_longer - (to make data in correct format for time-series line graphs)
vacancy_interval_counts_sem_subjects <- vacancy_interval_counts_sem_subject %>%
pivot_longer(!Subject, names_to = "Semester", values_to = "Count")
vacancy_interval_counts_sem_subjects


# #put numbers ahead of month name (so plots in order)
# vacancy_interval_counts_sem_region$Semester[vacancy_interval_counts_sem_region$Semester == "Jul"] <- "01 Jul"
# vacancy_interval_counts_sem_region$Semester[vacancy_interval_counts_sem_region$Semester == "Aug"] <- "02 Aug"

#libraries
library(ideacolors)
library(ideadata)

#line graph
l_subject_sem <- vacancy_interval_counts_sem_subjects %>%
  ggplot(aes(x=Semester, y=Count, group = Subject, color = Subject)) +
 geom_line() +
    #scale_color_viridis(discrete = TRUE) +
    #ggtitle("Number of Vacancies for Each Month by Subject") +
    #theme_ipsum() +
    #ylab("Number of Vacancies SY 23-24")

 scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   #theme(legend.position="none") +             #removes legend  (REF:https://r-charts.com/ggplot2/legend/ )
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Number of Vacancies",
       title = "Number of Vacancies by Subject",
       subtitle = "for Each Semester for SY 23-24")

l_subject_sem

```




