---
title: "Part 1 Staffing/Vacancies Measure of Central Tendency"
author: Maura Carter
date: 10-03-2024
output: html_notebook
---

1. Summative Analysis of Vacancies

Include central tendency and variation by subject, grade, grade-subject, campus, campus-subject, region, region-subject

a) subject    (col: course credit type)          
b) grade 
c) grade-subject
d) campus
e) campus-subject
f) region
g) region-subject




#1) How long are vacancies (median and mean and SD)?
#2) How many vacancies (median, mean and SD)?
#3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
#4) Add box plots and histograms. 


#CHECKLIST - (Both VACANCIES and FMLA outputs)

#VACANCIES
a) subject    (col: course credit type)
 YES #1) How long are vacancies (median and mean and SD)? 
 YES #2) How many vacancies (median, mean and SD)?
  YES #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
BAR/HIST  #4) Add box plots and histograms. 


b) grade
 YES #1) How long are vacancies (median and mean and SD)?
 YES #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
 BAR #4) Add box plots and histograms. 

c) grade-subject
  YES #1) How long are vacancies (median and mean and SD)?
  YES #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
  BAR #4) Add box plots and histograms. 


d) campus
  YES #1) How long are vacancies (median and mean and SD)?
  YES #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
 BAR  #4) Add box plots and histograms. 


e) campus-subject
  YES #1) How long are vacancies (median and mean and SD)?
  YES #2) How many vacancies (median, mean and SD)?
 #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
  BAR #4) Add box plots and histograms. 


f) region
 YES #1) How long are vacancies (median and mean and SD)?
 YES #2) How many vacancies (median, mean and SD)?
  YES #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
 BAR/Hist #4) Add box plots and histograms. 


g) region-subject
 YES #1) How long are vacancies (median and mean and SD)?
 YES #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
 BAR #4) Add box plots and histograms. 


#FMLA
a) subject    (col: course credit type)
 YES #1) How long are vacancies (median and mean and SD)?
 YES #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
 BAR/hist #4) Add box plots and histograms. 


b) **grade
  #1) How long are vacancies (median and mean and SD)?
  #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
  #4) Add box plots and histograms. 

c) **grade-subject
  #1) How long are vacancies (median and mean and SD)?
  #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
  #4) Add box plots and histograms. 


d) campus
  YES #1) How long are vacancies (median and mean and SD)?
  YES #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
  BAR #4) Add box plots and histograms. 


e) campus-subject
  #1) How long are vacancies (median and mean and SD)?
  #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
  #4) Add box plots and histograms. 


f) region
  YES #1) How long are vacancies (median and mean and SD)?
  YES #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
  BAR/hist #4) Add box plots and histograms. 


g) region-subject
 YES #1) How long are vacancies (median and mean and SD)?
 YES #2) How many vacancies (median, mean and SD)?
  #3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
 BAR #4) Add box plots and histograms. 


# how to install ideadata package
https://rdrr.io/github/idea-analytics/ideadata/f/README.Rmd
``` {r install, eval=FALSE}

# install.packages("remotes") 
library(remotes)
# remotes::install_github("idea-analytics/ideadata")
#remotes::install_github("idea-analytics/ideacolors")
library(ideacolors)
library(ideadata)
```


```{r merge}
#Merge PowerSchool data with data files
source("munge/merge_data.R")

#Glimpse to see columns/rows in the tables
#glimpse(courses_tm_fmla_staff) # !!! This is where we have total_days_out
#glimpse(jobvite_staffing_vacancies) # !!! This is where we have total_days_vacancy


#look at the tables in R
courses_tm_fmla_staff   #FMLA data (number of days off for FMLA)  #7081
jobvite_staffing_vacancies   #number of days vacancy   #872
#jobvite

#write to csv
#write.csv(courses_tm_fmla_staff,"C:\\Users\\maura.carter\\Documents\\GitHub\\Staffing_Trends_Performance_Vacancies\\courses_tm_fmla_staff.csv", row.names = FALSE)

#write.csv(jobvite_staffing_vacancies,"C:\\Users\\maura.carter\\Documents\\GitHub\\Staffing_Trends_Performance_Vacancies\\jobvite_staffing_vacancies.csv", row.names = FALSE)

#read into R from a .csv
# jobvite_staffing_vacancies2 <- read.csv("C:\\Users\\maura.carter\\Documents\\GitHub\\Staffing_Trends_Performance_Vacancies\\jobvite_staffing_vacancies.csv", header = TRUE)
# jobvite_staffing_vacancies2


join_time_cols <- left_join(grade_fmla_data, courses_tm_fmla_staff, by = "employee_id") %>%
  mutate(`Total Days FMLA` = total_days_out) %>%
  select(employee_id, Grade, Subject, Region, Campus, leave_start_date, leave_end_date, fmla_days_out, total_days_out)
join_time_cols

```

#F) Region
```{r}

#instructions
#1) How long are vacancies (median and mean and SD)?
#2) How many vacancies (median, mean and SD)?
#3) What is the most # of vacancies at one "time" (time = week, month, quarter, semester)?
#4) Add box plots and histograms. 

#-----------------------------------------

#1) How long are vacancies (median and mean and SD)?


#f-1) region - VACANCY
region_median_mean_sd <-jobvite_staffing_vacancies %>%
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  select(Region, total_days_vacancy) %>%
  group_by(Region)  %>%
  summarise(Median = median(total_days_vacancy),
            Mean = mean(total_days_vacancy),
            SD = sd(total_days_vacancy)) 
  # count()
region_median_mean_sd


#change data to numeric
# jobvite_staffing_vacancies$employee_id <- as.numeric(jobvite_staffing_vacancies$employee_id)
# jobvite_staffing_vacancies$total_days_vacancy <- as.numeric(jobvite_staffing_vacancies$total_days_vacancy)

#------------------------------------------------------

#f-1) region - FMLA

#Add Regions to the FMLA data
#get school number and region from schools and regions tables, join to FMLA table 
schools <- ideadata::get_schools() %>%
  mutate(school_number = SchoolNumber) %>%
  select(school_number, RegionAltID) %>%
  collect() 
schools

region <- get_table(.table_name = "Regions", .database_name = "PROD1", 
        .schema = "Schools", .server_name = "RGVPDSD-DWPRD1") %>%          #[RGVPDSD-DWPRD1].[PROD1].[Schools].[Regions]
  mutate(region_id = RegionID) %>%
  select(region_id, RegionDescription, State)
region

#join data
schools_FMLA <- left_join(courses_tm_fmla_staff, schools, by = "school_number") %>%
  mutate(region_id = RegionAltID)
schools_FMLA

schools_region_FMLA <- left_join(schools_FMLA, region, by = "region_id", copy = TRUE) %>%
  mutate(Region = RegionDescription)
schools_region_FMLA

#write.csv(jobvite_staffing_vacancies,"C:\\Users\\maura.carter\\Documents\\GitHub\\Staffing_Trends_Performance_Vacancies\\jobvite_staffing_vacancies.csv", row.names = FALSE)



#Median, Mean, Mode: FMLA
region_FMLA_median_mean_sd <-schools_region_FMLA %>%
  mutate(Region = RegionDescription) %>%
  filter(Region == "Austin" |
           Region == "El Paso" |
           Region == "Greater Houston Area" |
           Region == "Lower Valley"|
           Region == "Upper Valley"|
           Region == "Mid Valley" |
           Region == "Permian Basin" |
           Region == "West San Antonio" |
           Region == "East San Antonio"  |
           Region == "Tarrant County") %>%
  select(Region, total_days_out) %>%
  filter(total_days_out >0) %>%
  group_by(Region)  %>%
  summarise(Median = median(total_days_out),
            Mean = mean(total_days_out),
            SD = sd(total_days_out)) 
  # count()
region_FMLA_median_mean_sd


#distinct regions
distinct_regions <- schools_region_FMLA %>%
  mutate(Region = RegionDescription) %>%
  select(Region) %>%
  distinct()
distinct_regions

```

#Region
#2) How many vacancies (median, mean and SD)?
```{r}

#2) How many vacancies are there? Count
#f-2 (region)
region_vacancy_count <-jobvite_staffing_vacancies %>%
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  select(Region) %>%
  group_by(Region)  %>%
  summarise(`Number of Vacancies` = n()) 
region_vacancy_count


org_vacancy_count_mean_median_SD_byRegion <- region_vacancy_count %>%
  summarise(`Median Over Regions` = median(`Number of Vacancies`),
            `Mean Over Regions` = mean(`Number of Vacancies`),
            `SD Over Regions` = sd(`Number of Vacancies`)) 
  
org_vacancy_count_mean_median_SD_byRegion


#---------------------------------------------

#f-2 (region)
region_fmla_count <-schools_region_FMLA %>%
 mutate(Region = RegionDescription) %>%
  filter(Region == "Austin" |
           Region == "El Paso" |
           Region == "Greater Houston Area" |
           Region == "Lower Valley"|
           Region == "Upper Valley"|
           Region == "Mid Valley" |
           Region == "Permian Basin" |
           Region == "West San Antonio" |
           Region == "East San Antonio"  |
           Region == "Tarrant County") %>%
  filter(total_days_out >0) %>%
  select(Region) %>%
  group_by(Region)  %>%
  summarise(`Number of Leaves for FMLA` = n())
region_fmla_count


org_fmla_count_mean_median_SD_byRegion <- region_fmla_count %>%
  summarise(`Median Over Regions` = median(`Number of Leaves for FMLA`),
            `Mean Over Regions` = mean(`Number of Leaves for FMLA`),
            `SD Over Regions` = sd(`Number of Leaves for FMLA`)) 
  
org_fmla_count_mean_median_SD_byRegion





```



#Region
#4) Add box plots and Histograms.
```{r}
#4) Add box plots and histograms.  
#region
#f-4)   

#1) How long are vacancies/FMLA

#VACANCY
#Data Prep
hist_prep_data <- jobvite_staffing_vacancies %>%
  mutate("Vacancy Length in Days" = total_days_vacancy) %>%
  select(region.x, `Vacancy Length in Days`) 
hist_prep_data  

#Austin
Austin_Region <- hist_prep_data %>%
  filter(region.x == "AUSTIN REGION")
Austin_Region 

hist(Austin_Region$`Vacancy Length in Days`)

#El Paso
El_Paso_Region <- hist_prep_data %>%
  filter(region.x == "EL PASO REGION")
El_Paso_Region 

hist(El_Paso_Region$`Vacancy Length in Days`)

#Greater Houston
Greater_Houston_Region <- hist_prep_data %>%
  filter(region.x == "GREATER HOUSTON REGION")
Greater_Houston_Region

hist(Greater_Houston_Region$`Vacancy Length in Days`)

#Lower Valley RGV
Lower_Valley_RGV <- hist_prep_data %>%
  filter(region.x == "LOWER VALLEY RGV")
Lower_Valley_RGV

hist(Lower_Valley_RGV$`Vacancy Length in Days`)

#Upper Valley RGV
Upper_Valley_RGV <- hist_prep_data %>%
  filter(region.x == "UPPER VALLEY RGV")
Upper_Valley_RGV 

hist(Upper_Valley_RGV$`Vacancy Length in Days`)

#Mid Valley RGV
Mid_Valley_RGV <- hist_prep_data %>%
  filter(region.x == "MID VALLEY RGV")
Mid_Valley_RGV 

hist(Mid_Valley_RGV$`Vacancy Length in Days`)

#Permian Basin Region
Permian_Basin_Region <- hist_prep_data %>%
  filter(region.x == "PERMIAN BASIN REGION")
Permian_Basin_Region 

hist(Permian_Basin_Region$`Vacancy Length in Days`)

#San Antonio
San_Antonio_Region <- hist_prep_data %>%
  filter(region.x == "SAN ANTONIO REGION")
San_Antonio_Region 

hist(San_Antonio_Region$`Vacancy Length in Days`)

#Tarrant County
Tarrant_County_Region <- hist_prep_data %>%
  filter(region.x == "TARRANT COUNTY REGION")
Tarrant_County_Region

hist(Tarrant_County_Region$`Vacancy Length in Days`)

#EXAMPLE Historgram
# not_first_yr <- data1 %>%
#   group_by(EmployeeID, FirstYearTeacher) %>%
#   filter(FirstYearTeacher == 0) %>%
#   summarize(Percent_Mastery = mean(Mastery, na.rm = TRUE))
# not_first_yr #approx. 1124 Non-first year teachers in our dataset
# 
# hist(not_first_yr$Percent_Mastery)


#---------------------------------
#FMLA
schools_region_FMLA

hist_prep_region_fmla_length <- schools_region_FMLA %>%
  mutate(Region = RegionDescription) %>%
  mutate(`Length of FMLA in Days` = total_days_out) %>%
  filter(Region == "Austin" |
            Region == "El Paso" |
            Region == "Greater Houston Area" |
            Region == "Lower Valley"|
            Region == "Upper Valley"|
            Region == "Mid Valley" |
            Region == "Permian Basin" |
            Region == "West San Antonio" |
            Region == "East San Antonio"  |
            Region == "Tarrant County") %>%
   filter(total_days_out >0) %>%
   select(Region, `Length of FMLA in Days`) 
hist_prep_region_fmla_length
  

#facet_wrap(~ align + gender)
#Austin
`Austin` <- hist_prep_region_fmla_length %>%
  filter(Region == "Austin")
`Austin`
hist(`Austin`$`Length of FMLA in Days`)

#El Paso
`El Paso` <- hist_prep_region_fmla_length %>%
  filter(Region == "El Paso")
`El Paso`
hist(`El Paso`$`Length of FMLA in Days`)

#Greater Houston Area
`Greater Houston Area` <- hist_prep_region_fmla_length %>%
  filter(Region == "Greater Houston Area")
`Greater Houston Area`
hist(`Greater Houston Area`$`Length of FMLA in Days`)

#Lower Valley RGV
`Lower Valley` <- hist_prep_region_fmla_length %>%
  filter(Region == "Lower Valley")
`Lower Valley`
hist(`Lower Valley`$`Length of FMLA in Days`)

#Upper Valley RGV
`Upper Valley` <- hist_prep_region_fmla_length %>%
  filter(Region == "Upper Valley")
`Upper Valley`
hist(`Upper Valley`$`Length of FMLA in Days`)

#Mid Valley RGV
`Mid Valley` <- hist_prep_region_fmla_length %>%
  filter(Region == "Mid Valley")
`Mid Valley`
hist(`Mid Valley`$`Length of FMLA in Days`)

#Permian Basin
`Permian Basin` <- hist_prep_region_fmla_length %>%
  filter(Region == "Permian Basin")
`Permian Basin`
hist(`Permian Basin`$`Length of FMLA in Days`)

#West San Antonio
`West San Antonio` <- hist_prep_region_fmla_length %>%
  filter(Region == "West San Antonio")
`West San Antonio`
hist(`West San Antonio`$`Length of FMLA in Days`)

#East San Antonio
`East San Antonio` <- hist_prep_region_fmla_length %>%
  filter(Region == "East San Antonio")
`East San Antonio`
hist(`East San Antonio`$`Length of FMLA in Days`)


#Tarrant County
`Tarrant County` <- hist_prep_region_fmla_length %>%
  filter(Region == "Tarrant County")
`Tarrant County`
hist(`Tarrant County`$`Length of FMLA in Days`)



```

#barchart (vacancy count)
#region
```{r}
#BAR
#vacancy counts


#2) count of vacancies - bar chart
# region_vacancy_count <-jobvite_staffing_vacancies %>%
#   mutate(Region = region.x) %>%
#   filter(Region == "AUSTIN REGION" |
#            Region == "EL PASO REGION" |
#            Region == "GREATER HOUSTON REGION" |
#            Region == "LOWER VALLEY RGV"|
#            Region == "UPPER VALLEY RGV"|
#            Region == "MID VALLEY RGV" |
#            Region == "PERMIAN BASIN REGION" |
#            Region == "SAN ANTONIO REGION" |
#            Region == "TARRANT COUNTY REGION") %>%
#   select(Region) %>%
#   group_by(Region)  %>%
#   summarise(`Number of Vacancies` = n()) 

#dataset name for counts
region_vacancy_count


plot_vacancy_count <- ggplot(region_vacancy_count, 
                             aes(x = `Number of Vacancies`, 
                                 y = reorder(Region, -`Number of Vacancies`),
                                 fill = Region)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   theme(legend.position="none") +
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Region",
       title = "Number of Staffing Vacancies by Region",
       subtitle = "for SY 23-24")

plot_vacancy_count

#EXAMPLE CODE
#REF: https://bookdown.org/dli/rguide/bar-graph.html#ggplot2-bar-graph

# ggplot(data = IB, aes(x = reorder(Browser, -Users), 
#                            y = Users, fill = Browser)) + 
#    geom_bar(stat = "identity") + 
#    labs(title = "2018 Internet Browser Users (in millions)",
#         x = "Internet Browser", y = "Users")

#----------------------------------------------
#BAR
#FMLA counts

# region_fmla_count <-schools_region_FMLA %>%
#  mutate(Region = RegionDescription) %>%
#   filter(Region == "Austin" |
#            Region == "El Paso" |
#            Region == "Greater Houston Area" |
#            Region == "Lower Valley"|
#            Region == "Upper Valley"|
#            Region == "Mid Valley" |
#            Region == "Permian Basin" |
#            Region == "West San Antonio" |
#            Region == "East San Antonio"  |
#            Region == "Tarrant County") %>%
#   filter(total_days_out >0) %>%
#   select(Region) %>%
#   group_by(Region)  %>%
#   summarise(`Number of Leaves for FMLA` = n())

#data for graph
region_fmla_count

plot_fmla_count_region <- ggplot(region_fmla_count, 
                             aes(x = `Number of Leaves for FMLA`, 
                                 y = reorder(Region, -`Number of Leaves for FMLA`),
                                 fill = Region)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   theme(legend.position="none") +
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Region",
       title = "Number of Teacher Leaves from FMLA Vacancies",
       subtitle = "by Region for SY 23-24")

plot_fmla_count_region

```


#-------------------------
#REGION
#Boxplot
```{r}
#data
subject_FMLA_median_mean

#VACANCY
#prep the data
region_vac <-jobvite_staffing_vacancies %>%
  mutate(Region = region.x) %>%
  mutate(`Number of Days of Vacancy` = total_days_vacancy) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  select(Region, `Number of Days of Vacancy`) 

region_vac


#Region - vacancy
#Add gitter
p_box_region_vacancy_count <- region_vac %>%
  ggplot(aes(x= `Number of Days of Vacancy`,
             y = Region, 
             #fill = as.factor(FirstYearTeacher),
             color =`Region`)) +
geom_boxplot(outlier.shape = NA, 
             alpha = .25,) +
  geom_jitter(size= 1, alpha =.75, width = .05) +

  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
  theme(legend.position="none") +         #removes the legend
  labs(
    #x= "Number of Staffing Vacancies",
      #y ="Region",
       title = "Number of Days of Vacancy by Region",
       subtitle = "for SY 23-24")


p_box_region_vacancy_count

#------------------------------
#FMLA - Region


#Region - vacancy
#Add gitter
p_box_region_fmla_count <- subject_FMLA_median_mean %>%   # (from the subject cleaning data table below)
  ggplot(aes(x= `Total Days FMLA`,
             y = Region, 
             #fill = as.factor(FirstYearTeacher),
             color =`Region`)) +
geom_boxplot(outlier.shape = NA, 
             alpha = .25,) +
  geom_jitter(size= 1, alpha =.75, width = .05) +

  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
  theme(legend.position="none") +         #removes the legend
  labs(
    #x= "Number of Staffing Vacancies",
      #y ="Region",
       title = "Number of Teacher Leaves from FMLA by Region",
       subtitle = "for SY 23-24")

p_box_region_fmla_count



```

#CAMPUS
```{r}
#look at data
courses_tm_fmla_staff   #FMLA data (number of days off for FMLA)
jobvite_staffing_vacancies 


#use "campus_upper" for the campus name

```

#CAMPUS 
#1) how long were vacancies/FMLA
```{r}
#1) How long are vacancies (median and mean and SD)?

distinct_campus <- jobvite_staffing_vacancies %>%
 mutate(Campus = campus_upper) %>%
    filter(Campus == "HQ RGV" |
           Campus == "HQ SAN ANTONIO"|
           Campus == "HQ TARRANT COUNTY") 
distinct_campus

#f-1) region - VACANCY
campus_median_mean_sd <-jobvite_staffing_vacancies %>%
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  mutate(Campus = campus_upper) %>%
    filter(Campus != "HQ RGV") %>%
    filter(Campus != "HQ SAN ANTONIO") %>% 
    filter(Campus != "HQ TARRANT COUNTY") %>%
  select(Campus, total_days_vacancy) %>%
  group_by(Campus)  %>%
  summarise(Median = median(total_days_vacancy),
            Mean = mean(total_days_vacancy),
            SD = sd(total_days_vacancy)) 
  # count()
campus_median_mean_sd


#change data to numeric
# jobvite_staffing_vacancies$employee_id <- as.numeric(jobvite_staffing_vacancies$employee_id)
# jobvite_staffing_vacancies$total_days_vacancy <- as.numeric(jobvite_staffing_vacancies$total_days_vacancy)

#------------------------------------------------------

#d-1) campus - FMLA

#Add Regions to the FMLA data
#get school number and region from schools and regions tables, join to FMLA table 
schools <- ideadata::get_schools() %>%
  mutate(school_number = SchoolNumber) %>%
  select(school_number, RegionAltID) %>%
  collect() 
schools

region <- get_table(.table_name = "Regions", .database_name = "PROD1", 
        .schema = "Schools", .server_name = "RGVPDSD-DWPRD1") %>%          #[RGVPDSD-DWPRD1].[PROD1].[Schools].[Regions]
  mutate(region_id = RegionID) %>%
  select(region_id, RegionDescription, State)
region

#join data
schools_FMLA <- left_join(courses_tm_fmla_staff, schools, by = "school_number") %>%
  mutate(region_id = RegionAltID)
schools_FMLA

schools_region_FMLA <- left_join(schools_FMLA, region, by = "region_id", copy = TRUE)
schools_region_FMLA

#Median, Mean, Mode: FMLA
campus_FMLA_median_mean_sd <-schools_region_FMLA %>%
  mutate(Region = RegionDescription) %>%
  filter(Region == "Austin" |
           Region == "El Paso" |
           Region == "Greater Houston Area" |
           Region == "Lower Valley"|
           Region == "Upper Valley"|
           Region == "Mid Valley" |
           Region == "Permian Basin" |
           Region == "West San Antonio" |
           Region == "East San Antonio"  |
           Region == "Tarrant County") %>%
  mutate(Campus = campus) %>%
  select(Campus, total_days_out) %>%
  filter(total_days_out >0) %>%
  group_by(Campus)  %>%
  summarise(Median = median(total_days_out),
            Mean = mean(total_days_out),
            SD = sd(total_days_out)) 
campus_FMLA_median_mean_sd


```

#D) Campus
#2) Counts - how many vacancies/FMLA leaves

```{r}
#CAMPUS

#2) How many vacancies are there? Count
#f-2 (campus)
campus_vacancy_count <-jobvite_staffing_vacancies %>%
  mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
   mutate(Campus = campus_upper) %>%
    filter(Campus != "HQ RGV") %>%
    filter(Campus != "HQ SAN ANTONIO") %>% 
    filter(Campus != "HQ TARRANT COUNTY") %>%
  select(Campus, total_days_vacancy) %>%
  group_by(Campus)  %>%
  summarise(`Number of Vacancies` = n()) 
campus_vacancy_count


org_vacancy_count_mean_median_SD_byCampus <- campus_vacancy_count %>%
  summarise(`Median Over Campuses` = median(`Number of Vacancies`),
            `Mean Over Campuses` = mean(`Number of Vacancies`),
            `SD Over Campuses` = sd(`Number of Vacancies`)) 
  
org_vacancy_count_mean_median_SD_byCampus


#---------------------------------------------

#2 (campus)
campus_fmla_count <-schools_region_FMLA %>%
 mutate(Region = RegionDescription) %>%
  filter(Region == "Austin" |
           Region == "El Paso" |
           Region == "Greater Houston Area" |
           Region == "Lower Valley"|
           Region == "Upper Valley"|
           Region == "Mid Valley" |
           Region == "Permian Basin" |
           Region == "West San Antonio" |
           Region == "East San Antonio"  |
           Region == "Tarrant County") %>%
  filter(total_days_out >0) %>%
   mutate(Campus = campus) %>%hj
  select(Campus) %>%
  group_by(Campus)  %>%
  summarise(`Number of Leaves for FMLA` = n())
campus_fmla_count


org_fmla_count_mean_median_SD_byCampus <- campus_fmla_count %>%
  summarise(`Median Over Campuses` = median(`Number of Leaves for FMLA`),
            `Mean Over Campuses` = mean(`Number of Leaves for FMLA`),
            `SD Over Campuses` = sd(`Number of Leaves for FMLA`)) 
  
org_fmla_count_mean_median_SD_byCampus




```

#D) Campus
#4) Histograms/graphs

```{r}
#Data Prep for campus histograms
hist_prep_data_campus <- jobvite_staffing_vacancies %>%
  mutate("Vacancy Length in Days" = total_days_vacancy) %>%
  mutate(Campus = campus_upper) %>%
   mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  select(Campus, `Vacancy Length in Days`) 
hist_prep_data_campus



#facet_wrap(~ align + gender)
#Austin
Austin_Region <- hist_prep_data %>%
  filter(region.x == "AUSTIN REGION")
Austin_Region 

hist(Austin_Region$`Vacancy Length in Days`)

#El Paso
El_Paso_Region <- hist_prep_data %>%
  filter(region.x == "EL PASO REGION")
El_Paso_Region 

hist(El_Paso_Region$`Vacancy Length in Days`)

#Greater Houston
Greater_Houston_Region <- hist_prep_data %>%
  filter(region.x == "GREATER HOUSTON REGION")
Greater_Houston_Region

hist(Greater_Houston_Region$`Vacancy Length in Days`)

#Lower Valley RGV
Lower_Valley_RGV <- hist_prep_data %>%
  filter(region.x == "LOWER VALLEY RGV")
Lower_Valley_RGV

hist(Lower_Valley_RGV$`Vacancy Length in Days`)

#Upper Valley RGV
Upper_Valley_RGV <- hist_prep_data %>%
  filter(region.x == "UPPER VALLEY RGV")
Upper_Valley_RGV 

hist(Upper_Valley_RGV$`Vacancy Length in Days`)

#Mid Valley RGV
Mid_Valley_RGV <- hist_prep_data %>%
  filter(region.x == "MID VALLEY RGV")
Mid_Valley_RGV 

hist(Mid_Valley_RGV$`Vacancy Length in Days`)

#Permian Basin Region
Permian_Basin_Region <- hist_prep_data %>%
  filter(region.x == "PERMIAN BASIN REGION")
Permian_Basin_Region 

hist(Permian_Basin_Region$`Vacancy Length in Days`)

#San Antonio
San_Antonio_Region <- hist_prep_data %>%
  filter(region.x == "SAN ANTONIO REGION")
San_Antonio_Region 

hist(San_Antonio_Region$`Vacancy Length in Days`)

#Tarrant County
Tarrant_County_Region <- hist_prep_data %>%
  filter(region.x == "TARRANT COUNTY REGION")
Tarrant_County_Region

hist(Tarrant_County_Region$`Vacancy Length in Days`)

```

#Campus
#4) Bar - Vacancy, FMLA 
```{r}
#data for graph
campus_fmla_count

#vacancy - campus





#-------------------------------
#FMLA  - campus
campus_fmla_count

plot_fmla_count_campus <- ggplot(campus_fmla_count, 
                             aes(x = `Number of Leaves for FMLA`, 
                                 y = reorder(Campus, -`Number of Leaves for FMLA`),
                                 fill = Campus)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   theme(legend.position="none") +
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Campus",
       title = "Number of Teacher Leaves from FMLA",
       subtitle = "by Campus for SY 23-24")

plot_fmla_count_campus

```






#A) SUBJECT

```{r}
#look at the tables in R
courses_tm_fmla_staff   #FMLA data (number of days off for FMLA)
jobvite_staffing_vacancies   #number of days vacancy
#jobvite

```

#A) subject 
#clean the data/prep the subject column "job_title" to be subject
```{r}

#vacancies data

subject <- jobvite_staffing_vacancies %>%
   mutate("Vacancy Length in Days" = total_days_vacancy) %>%
  mutate(Campus = campus_upper) %>%
  mutate(Subject = job_title) %>%
   mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  filter(Subject != "Executive Campus Leadership") %>%
   mutate(Campus = campus_upper) %>%
    filter(Campus != "HQ RGV") %>%
    filter(Campus != "HQ SAN ANTONIO") %>% 
    filter(Campus != "HQ TARRANT COUNTY") %>%
  select(employee_id, Subject, "Vacancy Length in Days")      #add in "campus_upper" to get campus name, "region.x" to get region name 
subject


#distinct subjects
subject_distinct <- subject %>%
  select(Subject) %>%
  distinct()
subject_distinct

#social studides
#math
#science
#english language arts

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Math"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Science"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - English Language Arts"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject$Subject[subject$Subject == "Teaching - Social Studies"] <- "Social Studies"


#Change data from character to numeric (col Hired)
#job_1920$Hired <- as.numeric(job_1920$Hired)

#Change data from character to numeric (col Hired)
subject$Subject <- as.character(subject$Subject)
subject


#distinct subjects
subject_distinct2 <- subject %>%
  select(Subject) %>%
  distinct()
subject_distinct2

```


#A) Subject - 
#1) how long were vacancies/FMLA
```{r}
#1) How long are vacancies (median and mean and SD)?

#A-1) Subject - VACANCY
subject_median_mean_sd <- subject %>%
  select(Subject, `Vacancy Length in Days`) %>%
  #filter(Subject != "English Language Arts") %>%
  group_by(Subject)  %>%
  summarise(Median = median(`Vacancy Length in Days`),
            Mean = mean(`Vacancy Length in Days`),
            SD = sd(`Vacancy Length in Days`)) 
  # count()
subject_median_mean_sd

#------------------------------------------------------
#A-1) Subject - FMLA

#Add Regions to the FMLA data
#get school number and region from schools and regions tables, join to FMLA table 
schools <- ideadata::get_schools() %>%
  mutate(school_number = SchoolNumber) %>%
  select(school_number, RegionAltID) %>%
  collect() 
schools

region <- get_table(.table_name = "Regions", .database_name = "PROD1", 
        .schema = "Schools", .server_name = "RGVPDSD-DWPRD1") %>%          #[RGVPDSD-DWPRD1].[PROD1].[Schools].[Regions]
  mutate(region_id = RegionID) %>%
  select(region_id, RegionDescription, State)
region

#join data
schools_FMLA <- left_join(courses_tm_fmla_staff, schools, by = "school_number") %>%
  mutate(region_id = RegionAltID) 
schools_FMLA

schools_region_FMLA <- left_join(schools_FMLA, region, by = "region_id", copy = TRUE) %>%
  mutate(Region = RegionDescription)
schools_region_FMLA

#Median, Mean, Mode: FMLA
subject_FMLA_median_mean <-schools_region_FMLA %>%
  mutate(Region = RegionDescription) %>%
  mutate(Campus = campus) %>%
  mutate(`Total Days FMLA` = total_days_out) %>%
  filter(Region == "Austin" |
           Region == "El Paso" |
           Region == "Greater Houston Area" |
           Region == "Lower Valley"|
           Region == "Upper Valley"|
           Region == "Mid Valley" |
           Region == "Permian Basin" |
           Region == "West San Antonio" |
           Region == "East San Antonio"  |
           Region == "Tarrant County") %>%
  mutate(Subject =course_credit_type) %>%
  filter(total_days_out > 0) %>%
  select(employee_id, Subject, Region, Campus, `Total Days FMLA`)
subject_FMLA_median_mean
  
#distinct subjects
subject_distinct_fmla <- subject_FMLA_median_mean %>%
  select(Subject) %>%
  distinct()
subject_distinct_fmla

#social studides
#math
#science
#english language arts

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_FMLA_median_mean$Subject[subject_FMLA_median_mean$Subject == "MATH"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_FMLA_median_mean$Subject[subject_FMLA_median_mean$Subject == "SCI"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_FMLA_median_mean$Subject[subject_FMLA_median_mean$Subject == "ELA"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_FMLA_median_mean$Subject[subject_FMLA_median_mean$Subject == "SS"] <- "Social Studies"


#Change data from character to numeric (col Hired)
subject_FMLA_median_mean$Subject <- as.character(subject_FMLA_median_mean$Subject)
subject_FMLA_median_mean

#write.csv(subject_FMLA_median_mean,"C:\\Users\\maura.carter\\Documents\\GitHub\\Staffing_Trends_Performance_Vacancies\\subject_FMLA_median_mean.csv", row.names = FALSE)

#-------------------------

#distinct subjects
subject_distinct2_FMLA <- subject %>%
  select(Subject) %>%
  distinct()
subject_distinct2_FMLA

#-----------------------------
#summary stats - FMLA/Subject
subject_FMLA_median_mean_sd_chart <- subject_FMLA_median_mean %>%
  select(Subject, `Total Days FMLA`) %>%
  filter(`Total Days FMLA` >0) %>%
  group_by(Subject)  %>%
  summarise(Median = median(`Total Days FMLA`),
            Mean = mean(`Total Days FMLA`),
            SD = sd(`Total Days FMLA`)) 
subject_FMLA_median_mean_sd_chart

```

#A) Subject
#2) Counts - how many vacancies/FMLA leaves

```{r}
#SUBJECT

#2) How manyare there? Count
#A-2 (Subject)

#VACANCY
subject_vacancy_count <-subject %>%
  select(Subject, `Vacancy Length in Days`) %>%
  group_by(Subject)  %>%
  summarise(`Number of Vacancies` = n()) 
subject_vacancy_count


org_vacancy_count_mean_median_SD_bySubject <- subject_vacancy_count %>%
  summarise(`Median Over Subjects` = median(`Number of Vacancies`),
            `Mean Over Subjects` = mean(`Number of Vacancies`),
            `SD Over Subjects` = sd(`Number of Vacancies`)) 
  
org_vacancy_count_mean_median_SD_bySubject


#---------------------------------------------

#a-2 (subject)
#FMLA
subject_fmla_count <-subject_FMLA_median_mean_sd %>%
  #mutate(`Number of Days of FMLA` = total_days_out) %>%
  select(Subject) %>%
  group_by(Subject)  %>%
  summarise(`Number of Leaves for FMLA` = n())
subject_fmla_count


org_fmla_count_mean_median_SD_bySubject <- subject_fmla_count %>%
  summarise(`Median Over Subject` = median(`Number of Leaves for FMLA`),
            `Mean Over Subject` = mean(`Number of Leaves for FMLA`),
            `SD Over Subject` = sd(`Number of Leaves for FMLA`)) 
  
org_fmla_count_mean_median_SD_bySubject




```
#A) subject
#4) histograms

```{r}
#Data prep for Subjects histograms

#vacancies data

subject


hist_prep_data_subject_VAC <- subject %>%
  # mutate(Campus = campus_upper) %>%
  #  mutate(Region = region.x) %>%
  # filter(Region == "AUSTIN REGION" |
  #          Region == "EL PASO REGION" |
  #          Region == "GREATER HOUSTON REGION" |
  #          Region == "LOWER VALLEY RGV"|
  #          Region == "UPPER VALLEY RGV"|
  #          Region == "MID VALLEY RGV" |
  #          Region == "PERMIAN BASIN REGION" |
  #          Region == "SAN ANTONIO REGION" |
  #          Region == "TARRANT COUNTY REGION") %>%
  select(Subject, `Vacancy Length in Days`) 
hist_prep_data_subject_VAC



#facet_wrap(~ align + gender)
#MATH
`Math` <- hist_prep_data_subject_VAC %>%
  filter(Subject == "Math")
`Math`
hist(`Math`$`Vacancy Length in Days`)

#SCIENCE
`Science` <- hist_prep_data_subject_VAC %>%
  filter(Subject == "Science")
`Science`
hist(`Science`$`Vacancy Length in Days`)
#MATH

`English Language Arts` <- hist_prep_data_subject_VAC %>%
  filter(Subject == "English Language Arts")
`English Language Arts`
hist(`English Language Arts`$`Vacancy Length in Days`)

#MATH
`Social Studies` <- hist_prep_data_subject_VAC %>%
  filter(Subject == "Social Studies")
`Social Studies`
hist(`Social Studies`$`Vacancy Length in Days`)



#------------------------------------

#FMLA data

hist_prep_data_subject_FMLA <- subject_FMLA_median_mean_sd %>%
  mutate("Total Days of FMLA" = total_days_out) %>%
  # mutate(Campus = campus_upper) %>%
  #  mutate(Region = region.x) %>%
  # filter(Region == "AUSTIN REGION" |
  #          Region == "EL PASO REGION" |
  #          Region == "GREATER HOUSTON REGION" |
  #          Region == "LOWER VALLEY RGV"|
  #          Region == "UPPER VALLEY RGV"|
  #          Region == "MID VALLEY RGV" |
  #          Region == "PERMIAN BASIN REGION" |
  #          Region == "SAN ANTONIO REGION" |
  #          Region == "TARRANT COUNTY REGION") %>%
  select(Subject, `Total Days of FMLA`) 
hist_prep_data_subject_FMLA



#facet_wrap(~ align + gender)
#MATH
Math <- hist_prep_data_subject_FMLA %>%
  filter(Subject == "Math")
Math
hist(Math$`Total Days of FMLA`)

#SCIENCE
Science <- hist_prep_data_subject_FMLA %>%
  filter(Subject == "Science")
Science
hist(Science$`Total Days of FMLA`)
#MATH

English_Language_Arts <- hist_prep_data_subject_FMLA %>%
  filter(Subject == "English Language Arts")
English_Language_Arts
hist(English_Language_Arts$`Total Days of FMLA`)

#MATH
Social_Studies <- hist_prep_data_subject_FMLA %>%
  filter(Subject == "Social Studies")
Social_Studies
hist(Social_Studies$`Total Days of FMLA`)

```


#4) BAR
#A) Subject 
```{r}

#VACANCY - subject
#dataset name for counts
subject_vacancy_count


plot_vacancy_count_subject <- ggplot(subject_vacancy_count, 
                             aes(x = `Number of Vacancies`, 
                                 y = reorder(Subject, -`Number of Vacancies`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   theme(legend.position="none") +
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Subject",
       title = "Number of Staffing Vacancies by Subject",
       subtitle = "for SY 23-24")

plot_vacancy_count_subject


#--------------------

#FMLA - subject
subject_fmla_count 

plot_fmla_count_subject <- ggplot(subject_fmla_count, 
                             aes(x = `Number of Leaves for FMLA`, 
                                 y = reorder(Subject, -`Number of Leaves for FMLA`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   theme(legend.position="none") +
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Subject",
       title = "Number of Teacher Leaves from FMLA",
       subtitle = "by Subject for SY 23-24")

plot_fmla_count_subject



```

#BOXPLOT
#SUBJECT
```{r}

#data

#VACANCY - subject
#vacancy data
subject


#prep the data
subject_vac <-subject %>%
  select(Subject, `Vacancy Length in Days`) 

subject_vac


#Subject - vacancy
#Add gitter
p_box_subject_vacancy_count <- subject_vac %>%
  ggplot(aes(x= `Vacancy Length in Days`,
             y = Subject, 
             #fill = as.factor(FirstYearTeacher),
             color =`Subject`)) +
geom_boxplot(outlier.shape = NA, 
             alpha = .25,) +
  geom_jitter(size= 1, alpha =.75, width = .05) +

  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
  theme(legend.position="none") +         #removes the legend
  labs(
    #x= "Number of Staffing Vacancies",
      #y ="Region",
       title = "Number of Days of Vacancy by Subject",
       subtitle = "for SY 23-24")

p_box_subject_vacancy_count

#------------------
#FMLA


#Region - vacancy
#Add gitter
p_box_subject_fmla_count <- subject_FMLA_median_mean %>%   # (from the subject cleaning data table below)
  ggplot(aes(x= `Total Days FMLA`,
             y = Subject, 
             #fill = as.factor(FirstYearTeacher),
             color =`Subject`)) +
geom_boxplot(outlier.shape = NA, 
             alpha = .25,) +
  geom_jitter(size= 1, alpha =.75, width = .05) +

  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
  theme(legend.position="none") +         #removes the legend
  labs(
    #x= "Number of Staffing Vacancies",
      #y ="Region",
       title = "Number of Teacher Leaves from FMLA by Subject",
       subtitle = "for SY 23-24")

p_box_subject_fmla_count




```



#REGION-SUBJECT

#1) how long?  (vacancies/fmla)
```{r}

#1) How long are vacancies (median and mean and SD)?

#vacancy data

#region-subject
subject_region <- jobvite_staffing_vacancies %>%
   mutate("Vacancy Length in Days" = total_days_vacancy) %>%
  mutate(Campus = campus_upper) %>%
  mutate(Subject = job_title) %>%
   mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  filter(Subject != "Executive Campus Leadership") %>%
  select(employee_id, Region, Subject, "Vacancy Length in Days")      #add in "campus_upper" to get campus name, "region.x" to get region name 
subject_region

#change names of subjects to exclude "teacher" 
#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_region$Subject[subject_region$Subject == "Teaching - Math"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_region$Subject[subject_region$Subject == "Teaching - Science"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_region$Subject[subject_region$Subject == "Teaching - English Language Arts"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_region$Subject[subject_region$Subject == "Teaching - Social Studies"] <- "Social Studies"


#Change data from character to numeric (col Hired)
#job_1920$Hired <- as.numeric(job_1920$Hired)

#Change data from character to numeric (col Hired)
subject_region$Subject <- as.character(subject_region$Subject)
subject_region


#distinct subjects
subject_region_distinct2 <- subject_region %>%
  select(Subject) %>%
  distinct()
subject_region_distinct2

#------------------
#1) how long?

#subject-region - VACANCY
region_subject_median_mean_sd <-subject_region %>%  #(df "subject_region" from above that was cleaned and filtered for region, subject)
  # filter(Region == "AUSTIN REGION" |
  #          Region == "EL PASO REGION" |
  #          Region == "GREATER HOUSTON REGION" |
  #          Region == "LOWER VALLEY RGV"|
  #          Region == "UPPER VALLEY RGV"|
  #          Region == "MID VALLEY RGV" |
  #          Region == "PERMIAN BASIN REGION" |
  #          Region == "SAN ANTONIO REGION" |
  #          Region == "TARRANT COUNTY REGION") %>%
  select(Region, Subject, `Vacancy Length in Days`) %>%
  group_by(Region, Subject)  %>%
   summarise(Median = median(`Vacancy Length in Days`),
             Mean = mean(`Vacancy Length in Days`),
             SD = sd(`Vacancy Length in Days`)) 

region_subject_median_mean_sd

#FMLA - #1) how long?

#data
subject_FMLA_median_mean

region_subject_summary_stats_FMLA <-subject_FMLA_median_mean %>%  #(df "subject_FMLA_median_mean" from above that was cleaned and filtered for region, subject)
  select(Region, Subject, `Total Days FMLA`) %>%
  group_by(Region, Subject)  %>%
   summarise(Median = median(`Total Days FMLA`),
             Mean = mean(`Total Days FMLA`),
             SD = sd(`Total Days FMLA`)) 

region_subject_summary_stats_FMLA



```


#REGION-SUBJECT
#2) how many? counts (vacancy/fmla)

```{r}
#2) How many are there? Count
# (Region-Subject)

#VACANCY
region_subject_vacancy_count <-subject_region %>%
  select(Region, Subject, `Vacancy Length in Days`) %>%
  group_by(Region, Subject)  %>%
  summarise(`Number of Vacancies` = n()) 
region_subject_vacancy_count


org_vacancy_count_mean_median_SD_bySubject_region <- region_subject_vacancy_count %>%
  summarise(`Median Over Region & Subject` = median(`Number of Vacancies`),
            `Mean Over Region & Subject` = mean(`Number of Vacancies`),
            `SD Over Region & Subject` = sd(`Number of Vacancies`)) 
  
org_vacancy_count_mean_median_SD_bySubject_region

#-------------------

#FMLA - #2) how many/count?
#region-subject

#data
subject_FMLA_median_mean

region_subject_FMLA_count <- subject_FMLA_median_mean %>%
  mutate(`Total FMLA` = `Total Days FMLA`) %>%
  select(Region, Subject, `Total FMLA`) %>%
  group_by(Region, Subject) %>%
  summarise(`Total FMLA` = n())
region_subject_FMLA_count


```


#GRAPHS
#Region-Subject

#BAR
```{r}

#VACANCY     (region-subject)
#dataset name for counts
region_subject_vacancy_count

#Bar plot
plot_vacancy_count_subject_reg <- ggplot(region_subject_vacancy_count, 
                             aes(x = `Number of Vacancies`, 
                                 y = reorder(Region, -`Number of Vacancies`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity",
           position = "dodge") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +      #adds a grid to the background (instead of keeping it blank white)
  #guides(fill = "none", color = "none") +
  # theme(legend.position="none") +      #removes legend
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Region",
       title = "Number of Staffing Vacancies by Region & Subject",
       subtitle = "for SY 23-24")

plot_vacancy_count_subject_reg

#-----------------------------
#data
region_subject_FMLA_count

#Bar plot
plot_fmla_count_subject_reg <- ggplot(region_subject_FMLA_count, 
                             aes(x = `Total FMLA`, 
                                 y = reorder(Region, -`Total FMLA`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity",
           position = "dodge") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +      #adds a grid to the background (instead of keeping it blank white)
  #guides(fill = "none", color = "none") +
  # theme(legend.position="none") +      #removes legend
  labs(
    x= "Number of Leaves from FMLA",
      y ="Region",
       title = "Number of Teacher Leaves from FMLA",
       subtitle = "by Region & Subject for SY 23-24")

plot_fmla_count_subject_reg


```


#BOXPLOT
#REGION-SUBJECT
```{r}

#data
#vacancy data
subject_region


#prep the data
subject_region_vac <-subject_region %>%
  select(Region, Subject, `Vacancy Length in Days`) 
subject_region_vac


#Subject - vacancy
#Add gitter
p_box_subject_vacancy_count <- subject_region_vac %>%
  ggplot(aes(x= `Vacancy Length in Days`,
             y = Region, 
             #fill = as.factor(FirstYearTeacher),
             fill =`Subject`,
             color = Subject)) +
geom_boxplot(outlier.shape = NA, 
             alpha = .25,) +
  geom_jitter(size= 1, alpha =.75, width = .05) +

  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
 # theme(legend.position="none") +         #removes the legend
  labs(
    #x= "Number of Staffing Vacancies",
      #y ="Region",
       title = "Number of Days of Vacancy by Region",
       subtitle = "for all Subjects SY 23-24")

p_box_subject_vacancy_count

#-------------------------
#FMLA
#region-subject

#data
region_subject_FMLA_count

#prep the data
subject_region_vac <-subject_region %>%
  select(Region, Subject, `Vacancy Length in Days`) 
subject_region_vac


#Region-Subject - FMLA
#Add gitter
p_box_reg_subject_fmla_count <- subject_FMLA_median_mean %>%
  ggplot(aes(x= `Total Days FMLA`,
             y = Region, 
             #fill = as.factor(FirstYearTeacher),
             fill =`Subject`,
             color = Subject)) +
geom_boxplot(outlier.shape = NA, 
             alpha = .25,) +
  geom_jitter(size= 1, alpha =.75, width = .05) +

  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
 # theme(legend.position="none") +         #removes the legend
  labs(
    x= "Number of FMLA Leaves",
      #y ="Region",
       title = "Teacher Leaves From FMLA Leaves by Region & Subject SY 23-24") #,
       #subtitle = "by Region & Subject SY 23-24")

p_box_reg_subject_fmla_count
```




#CAMPUS-SUBJECT
```{r}
#1) How long are vacancies (median and mean and SD)?
library(dplyr)
#Campus-subject
subject_camp <- jobvite_staffing_vacancies %>%
   mutate("Vacancy Length in Days" = total_days_vacancy) %>%
  mutate(Campus = campus_upper) %>%
  mutate(Subject = job_title) %>%
   mutate(Region = region.x) %>%
  filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  filter(Subject != "Executive Campus Leadership") %>%
    filter(Campus != "HQ RGV") %>%
    filter(Campus != "HQ SAN ANTONIO") %>% 
    filter(Campus != "HQ TARRANT COUNTY") %>%
  select(employee_id, Campus, Subject, `Vacancy Length in Days`)      #add in "campus_upper" to get campus name, "region.x" to get region name 
subject_camp

#change names of subjects to exclude "teacher" 
#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_camp$Subject[subject_camp$Subject == "Teaching - Math"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_camp$Subject[subject_camp$Subject == "Teaching - Science"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_camp$Subject[subject_camp$Subject == "Teaching - English Language Arts"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
subject_camp$Subject[subject_camp$Subject == "Teaching - Social Studies"] <- "Social Studies"


#Change data from character to numeric (col Hired)
#job_1920$Hired <- as.numeric(job_1920$Hired)

#Change data from character to numeric (col Hired)
subject_camp$Subject <- as.character(subject_camp$Subject)
subject_camp

#Campus-Subject    - VACANCY
#how long?
campus_subject_median_mean_sd <-subject_camp %>%
  group_by(Campus, Subject)  %>%
  summarise(Median = median(`Vacancy Length in Days`),
            Mean = mean(`Vacancy Length in Days`),
            SD = sd(`Vacancy Length in Days`)) 
  # count()
campus_subject_median_mean_sd


#change data to numeric
# jobvite_staffing_vacancies$employee_id <- as.numeric(jobvite_staffing_vacancies$employee_id)
# jobvite_staffing_vacancies$total_days_vacancy <- as.numeric(jobvite_staffing_vacancies$total_days_vacancy)

#---------------------------
#FMLA

#data
subject_FMLA_median_mean

#Campus-Subject    - FMLA
#how long?
campus_subject_median_mean_sd_FMLA <-subject_FMLA_median_mean %>%
  mutate(`FMLA Length in Days` = `Total Days FMLA`) %>%
  select(Campus, Subject, `FMLA Length in Days`) %>%
  group_by(Campus, Subject)  %>%
  summarise(Median = median(`FMLA Length in Days`),
            Mean = mean(`FMLA Length in Days`),
            SD = sd(`FMLA Length in Days`)) 
  # count()
campus_subject_median_mean_sd_FMLA










```

#CAMPUS-SUBJECT
#2) how many? counts (vacancy/fmla)

```{r}
#2) How manyare there? Count
#Campus-subject


#data
subject_camp

#VACANCY
#subjct_campus

camp_subject_vacancy_count <-subject_camp %>%
  select(Campus, Subject, `Vacancy Length in Days`) %>%
  group_by(Campus, Subject)  %>%
  summarise(`Number of Vacancies` = n()) 
camp_subject_vacancy_count


#not meaningful 

# org_vacancy_count_mean_median_SD_bySubject_campus <- camp_subject_vacancy_count %>%
#   summarise(`Median Over Campus & Subject` = median(`Number of Vacancies`),
#             `Mean Over Campus & Subject` = mean(`Number of Vacancies`),
#             `SD Over Campus & Subject` = sd(`Number of Vacancies`)) 
#   
# org_vacancy_count_mean_median_SD_bySubject_campus


#----------------------------
#FMLA - subject_campus

campus_subject_fmla_count <-subject_FMLA_median_mean %>%
  mutate(`Total FMLA` =`Total Days FMLA`) %>%
  select(Campus, Subject, `Total FMLA`) %>%
  group_by(Campus, Subject)  %>%
  summarise(`Total FMLA` = n()) 
campus_subject_fmla_count


```

#4) BAR
#A) Subject 
```{r}

#CAMPUS-SUBJECT

#vacancy

#dataset name for counts
camp_subject_vacancy_count

#campus-subject
plot_vacancy_count_subject_camp <- ggplot(camp_subject_vacancy_count, 
                             aes(x = `Number of Vacancies`, 
                                 y = reorder(Campus, -`Number of Vacancies`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
  # theme(legend.position="none") +       #removes legend
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Campus",
       title = "Number of Staffing Vacancies by Campus",
       subtitle = "and Subject for SY 23-24")

plot_vacancy_count_subject_camp

#-----------------------------------
#FMLA
#campus-subject
plot_fmla_total_days_subject_camp <- ggplot(subject_FMLA_median_mean, 
                             aes(x = `Total Days FMLA`, 
                                 y = reorder(Campus, -`Total Days FMLA`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
  # theme(legend.position="none") +       #removes legend
  labs(
    x= "Number Days of FMLA",
      y ="Campus",
       title = "Number of Days of FMLA by Campus & Subject",
       subtitle = "for SY 23-24")

plot_fmla_total_days_subject_camp

#counts
#FMLA

plot_fmla_counts_subject_camp <- ggplot(campus_subject_fmla_count, 
                             aes(x = `Total FMLA`, 
                                 y = reorder(Campus, -`Total FMLA`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
  # theme(legend.position="none") +       #removes legend
  labs(
    x= "Number Leaves from FMLA",
      y ="Campus",
       title = "Number of Leaves from FMLA by Campus & Subject",
       subtitle = "for SY 23-24")

plot_fmla_counts_subject_camp

```


#GRADE

# (grade, grade-subject)
#clean the grade data 
```{r}
#vacancy data
jobvite_staffing_vacancies

grades_data <- jobvite_staffing_vacancies %>%
select(employee_id, region.x, campus_upper, department, job_title, total_days_vacancy)
grades_data


grade_data <- grades_data %>%
     mutate(`Vacancy Length in Days` = total_days_vacancy) %>%
  mutate(Campus = campus_upper) %>%
  mutate(Subject = job_title) %>%
   mutate(Region = region.x) %>%
  mutate(Grade = department) %>%
   filter(Region == "AUSTIN REGION" |
           Region == "EL PASO REGION" |
           Region == "GREATER HOUSTON REGION" |
           Region == "LOWER VALLEY RGV"|
           Region == "UPPER VALLEY RGV"|
           Region == "MID VALLEY RGV" |
           Region == "PERMIAN BASIN REGION" |
           Region == "SAN ANTONIO REGION" |
           Region == "TARRANT COUNTY REGION") %>%
  filter(Subject != "Executive Campus Leadership") %>%
    filter(Campus != "HQ RGV") %>%
    filter(Campus != "HQ SAN ANTONIO") %>%
    filter(Campus != "HQ TARRANT COUNTY") %>%
    select(employee_id, Region, Campus, Grade, Subject, `Vacancy Length in Days`)
grade_data

#change names of subjects to exclude "teacher" 
#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Subject[grade_data$Subject == "Teaching - Math"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Subject[grade_data$Subject == "Teaching - Science"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Subject[grade_data$Subject == "Teaching - English Language Arts"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Subject[grade_data$Subject == "Teaching - Social Studies"] <- "Social Studies"

grade_data

#Change data from character to numeric (col Hired)
grade_data$Subject <- as.character(grade_data$Subject)
grade_data

#----------------------------

#change department to grade

#distinct Grades
grade_distinct <- grade_data %>%
  select(Grade) %>%
  distinct()
grade_distinct

# Teacher: 1-5 Social Studies				
# Teacher: 1-5 Math				
# Teacher: 9-12 Science				
# Teacher: 9-12 Social Studies				
# Teacher: 9-12 Math				
# Teacher: 1-5 ELA				
# Teacher: 6-8 Social Studies				
# Teacher: 6-8 ELA				
# Teacher: 9-12 ELA				
# Teacher: 1-5 Social Studies/Science
# Teacher: 6-8 Math				
# Teacher: 6-8 Science				
# Teacher: 1-5 Science				
# Teacher: 6-8 Social Studies/Science				
# Teacher: 1-5 ELA/Social Studies		         #15 grade bins		
 


#change grades to exclude "teacher" and "sci/math/ela/ss"

#elementary
#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 1-5 Social Studies"] <- "1-5"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 1-5 Math"] <- "1-5"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 1-5 ELA"] <- "1-5"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 1-5 Science"] <- "1-5"

#middle
#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 6-8 Social Studies"] <- "6-8"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 6-8 Math"] <- "6-8"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 6-8 ELA"] <- "6-8"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 6-8 Science"] <- "6-8"

#high school
#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 9-12 Social Studies"] <- "9-12"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 9-12 Math"] <- "9-12"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 9-12 ELA"] <- "9-12"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 9-12 Science"] <- "9-12"

#other combos
#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 1-5 ELA/Social Studies"] <- "1-5"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 1-5 Social Studies/Science"] <- "1-5"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_data$Grade[grade_data$Grade == "Teacher: 6-8 Social Studies/Science"] <- "6-8"

grade_data_final <- grade_data
grade_data_final


```


#GRADE

#1) how long (vac/FMLA)
```{r}
#GRADE    - VACANCY
#1) how long?

#data
grade_data_final

#length vac
grade_median_mean_sd <-grade_data_final %>%
  select(Grade, `Vacancy Length in Days`) %>%
  group_by(Grade)  %>%
  summarise(Median = median(`Vacancy Length in Days`),
            Mean = mean(`Vacancy Length in Days`),
            SD = sd(`Vacancy Length in Days`)) 
  # count()
grade_median_mean_sd

#---------------------
#fmla

#prep the data
schools_region_FMLA

grade_fmla_data <- schools_region_FMLA %>%
  mutate(Region = RegionDescription) %>%
  mutate(Campus = campus) %>%
  mutate(`Total Days FMLA` = total_days_out) %>%
  filter(Region == "Austin" |
           Region == "El Paso" |
           Region == "Greater Houston Area" |
           Region == "Lower Valley"|
           Region == "Upper Valley"|
           Region == "Mid Valley" |
           Region == "Permian Basin" |
           Region == "West San Antonio" |
           Region == "East San Antonio"  |
           Region == "Tarrant County") %>%
  mutate(Subject =course_credit_type) %>%
  filter(total_days_out > 0) %>%
  select(employee_id, Subject, course_name, course_credit_type, campus_type, Region, Campus, `Total Days FMLA`, leave_start_date, leave_end_date)
grade_fmla_data
  
#distinct subjects
subject_distinct_fmla <- subject_FMLA_median_mean %>%
  select(Subject) %>%
  distinct()
subject_distinct_fmla

#social studides
#math
#science
#english language arts

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_fmla_data$Subject[grade_fmla_data$Subject == "MATH"] <- "Math"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_fmla_data$Subject[grade_fmla_data$Subject == "SCI"] <- "Science"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_fmla_data$Subject[grade_fmla_data$Subject == "ELA"] <- "English Language Arts"

#when col "Subject" is "teaching - social studies" replace it with "social studies".
grade_fmla_data$Subject[grade_fmla_data$Subject == "SS"] <- "Social Studies"


#Change data from character to numeric (col Hired)
grade_fmla_data$Subject <- as.character(grade_fmla_data$Subject)
grade_fmla_data

schools_region_FMLA
#distinct course_names
course_name_distinct <- grade_fmla_data %>%
  select(course_name) %>%
  distinct()
course_name_distinct

#write to csv, change course-name to "grade" manually, based on "course_name" and "campus_type".
write.csv(grade_fmla_data,"C:\\Users\\maura.carter\\Documents\\GitHub\\Staffing_Trends_Performance_Vacancies\\grade_fmla_data.csv", row.names = FALSE)


#1) how long? (fmla)

#data
grade_data_final

#length vac
grade_median_mean_sd_fmla <-grade_fmla_data_bins %>%
  select(Grade, `Total Days FMLA`) %>%
  group_by(Grade)  %>%
  summarise(Median = median(`Total Days FMLA`),
            Mean = mean(`Total Days FMLA`),
            SD = sd(`Total Days FMLA`)) 
  # count()
grade_median_mean_sd_fmla


#----------------------------------------

#join the grade_fmla_data to cleaned_grades table
grade_fmla_data
grade_fmla_data_bins


grade_fmla_data_bins_cols <- grade_fmla_data_bins %>%
  select(course_name, Grade) %>%
  group_by(course_name, Grade) %>%
  distinct(course_name) %>%
  ungroup()
grade_fmla_data_bins_cols

join_data_all <- left_join(grade_fmla_data, grade_fmla_data_bins_cols, by = "course_name")
join_data_all


#write to csv, change course-name to "grade" manually, based on "course_name" and "campus_type".
write.csv(join_data_all,"C:\\Users\\maura.carter\\Documents\\GitHub\\Staffing_Trends_Performance_Vacancies\\join_data_all.csv", row.names = FALSE)

```
#GRADE
#2) how many? counts (vacancy/fmla)

```{r}
#2) How manyare there? Count
#GRADE


#data
grade_data_final


#VACANCY
grade_vacancy_count <-grade_data_final %>%
  select(Grade, `Vacancy Length in Days`) %>%
  group_by(Grade)  %>%
  summarise(`Number of Vacancies` = n()) 
grade_vacancy_count



 org_vacancy_count_mean_median_SD_byGrade <- grade_vacancy_count %>%
   summarise(`Median Over Grade` = median(`Number of Vacancies`),
             `Mean Over Grade` = mean(`Number of Vacancies`),
             `SD Over Grade` = sd(`Number of Vacancies`)) 
   
 org_vacancy_count_mean_median_SD_byGrade
 
#---------------------------------
#FMLA
#grade
 
#bring in the data from csv
grade_fmla <- grade_fmla_data_bins 
grade_fmla

#2) how many?
grade_fmla_count <-grade_fmla %>%
  select(Grade, `Total Days FMLA`) %>%
  mutate(`Total FMLA` = `Total Days FMLA`) %>%
  group_by(Grade)  %>%
  summarise(`Total FMLA` = n()) 
grade_fmla_count



 org_fmla_count_mean_median_SD_byGrade <- grade_fmla_count %>%
   summarise(`Median Over Grade` = median(`Total FMLA`),
             `Mean Over Grade` = mean(`Total FMLA`),
             `SD Over Grade` = sd(`Total FMLA`)) 
   
 org_fmla_count_mean_median_SD_byGrade

```

#4) BAR
#GRADE 
```{r}

#GRADE

#vacancy

#dataset name for counts
grade_data_final
grade_vacancy_count

plot_vacancy_count_subject_camp <- ggplot(grade_vacancy_count, 
                             aes(x = `Number of Vacancies`, 
                                 y = reorder(Grade, -`Number of Vacancies`),
                                 fill = Grade)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   theme(legend.position="none") +       #removes legend
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Grade",
       title = "Number of Staffing Vacancies by Grade",
       subtitle = "for SY 23-24")

plot_vacancy_count_subject_camp
#fmla

#data
grade_fmla

plot_fmla_grade_count <- ggplot(grade_fmla_count, 
                             aes(x = `Total FMLA`, 
                                 y = reorder(Grade, -`Total FMLA`),
                                 fill = Grade)) + 
  geom_bar(stat = "identity") +
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
 #  theme(legend.position="none") +          #removes the legend
  labs(
    #x= "Number of FMLA Leaves",
      y ="Grade",
       title = "Number of Leaves from FMLA by Grade",
       subtitle = "for SY 23-24")

plot_fmla_grade_count


```

#GRADE-SUBJECT

#1) how long (vac/FMLA)
```{r}
#GRADE-subject    - VACANCY
#1) how long?

#data
grade_sub_data_final <- grade_data_final

#length vac
grade_sub_median_mean_sd <-grade_sub_data_final %>%
  select(Grade, Subject, `Vacancy Length in Days`) %>%
  group_by(Grade, Subject)  %>%
  summarise(Median = median(`Vacancy Length in Days`),
            Mean = mean(`Vacancy Length in Days`),
            SD = sd(`Vacancy Length in Days`)) 
  # count()
grade_sub_median_mean_sd


#--------------------
#fmla
#grade_subject

grade_fmla

#length of fmla
grade_sub_median_mean_sd_fmla <-grade_fmla %>%
  select(Grade, Subject, `Total Days FMLA`) %>%
  group_by(Grade, Subject)  %>%
  summarise(Median = median(`Total Days FMLA`),
            Mean = mean(`Total Days FMLA`),
            SD = sd(`Total Days FMLA`)) 
  # count()
grade_sub_median_mean_sd_fmla

```

#GRADE-subject
#2) how many? counts (vacancy/fmla)

```{r}
#2) How manyare there? Count
#GRADE-subject


#data
grade_data_final

#VACANCY
grade_sub_vacancy_count <-grade_data_final %>%
  select(Grade, Subject, `Vacancy Length in Days`) %>%
  group_by(Grade, Subject)  %>%
  summarise(`Number of Vacancies` = n()) 
grade_sub_vacancy_count



 org_vacancy_count_mean_median_SD_byGrade <- grade_vacancy_count %>%
   summarise(`Median Over Grade` = median(`Number of Vacancies`),
             `Mean Over Grade` = mean(`Number of Vacancies`),
             `SD Over Grade` = sd(`Number of Vacancies`)) 
   
 org_vacancy_count_mean_median_SD_byGrade
 
 #----------------------
 #fmla
 
 #grade-subject
 #counts/ how many leaves?
 
 #data
 grade_fmla

grade_sub_fmla_count <-grade_fmla %>%
  select(Grade, Subject, `Total Days FMLA`) %>%
  group_by(Grade, Subject)  %>%
  summarise(`Total Days FMLA` = n()) 
grade_sub_fmla_count


```





#4) BAR
#GRADE-SUBJECT
```{r}

#GRADE

#vacancy

#grade-subject

#dataset name for counts
grade_data_final
grade_sub_vacancy_count

plot_vacancy_count_subject_grade_camp <- ggplot(grade_sub_vacancy_count, 
                             aes(x = `Number of Vacancies`, 
                                 y = reorder(Grade, -`Number of Vacancies`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity",
           position = "dodge") +   #unstacks the bars; remove this to have stacked bars.
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   #theme(legend.position="none") +       #removes legend
  labs(
    #x= "Number of Staffing Vacancies",
      y ="Grade",
       title = "Number of Staffing Vacancies by Grade",
       subtitle = "and Subject for SY 23-24")

plot_vacancy_count_subject_grade_camp


#----------------------------
#fmla
#grade-subject

#data
grade_sub_fmla_count

plot_fmla_count_subject_grade <- ggplot(grade_sub_fmla_count, 
                             aes(x = `Total Days FMLA`, 
                                 y = reorder(Grade, -`Total Days FMLA`),
                                 fill = Subject)) + 
  geom_bar(stat = "identity",
           position = "dodge") +   #unstacks the bars; remove this to have stacked bars.
 
  scale_fill_idea(reverse = FALSE) +
  scale_color_idea() +
  ideacolors::theme_idea_min() +
   #ideacolors::theme_idea_light() +
  #guides(fill = "none", color = "none") +
   #theme(legend.position="none") +       #removes legend
  labs(
    x= "Number of Leaves From FMLA",
      y ="Grade",
       title = "Number of Leaves From FMLA by Grade",
       subtitle = "& Subject for SY 23-24")

plot_fmla_count_subject_grade


```


